\documentclass{article}
\usepackage[final]{neurips_2024}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{microtype}
\usepackage{float}
\usepackage{tikz}
\usepackage{pgf-pie}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

\makeatletter
\renewcommand{\section}{%
  \@startsection{section}{1}{\z@}%
                {-2.0ex \@plus -0.5ex \@minus -0.2ex}%
                { 1.5ex \@plus  0.3ex \@minus  0.2ex}%
                {\fontsize{15}{16.8}\selectfont\bf\raggedright}%
}
\renewcommand{\subsection}{%
  \@startsection{subsection}{2}{\z@}%
                {-1.8ex \@plus -0.5ex \@minus -0.2ex}%
                { 0.8ex \@plus  0.2ex}%
                {\fontsize{12}{14.4}\selectfont\bf\raggedright}%
}
\renewcommand{\subsubsection}{%
  \@startsection{subsubsection}{3}{\z@}%
                {-1.5ex \@plus -0.5ex \@minus -0.2ex}%
                { 0.5ex \@plus  0.2ex}%
                {\fontsize{10}{12}\selectfont\bf\raggedright}%
}
\makeatother

\lstdefinestyle{terminal}{
    backgroundcolor=\color{blue!5},
    basicstyle=\ttfamily\small,
    frame=single,
    rulecolor=\color{blue!30},
    breaklines=true,
    columns=fullflexible,
    keepspaces=true,
    showstringspaces=false
}


\title{Milestone Report: Safety Verification of Chiron IR using Constrained Horn Clauses}
\date{\today}

\begin{document}
\maketitle

\section{Up Next}

\subsection{Testing}
\begin{enumerate}[leftmargin=*]
\item \textbf{Metamorphic tests.} Generate semantically equivalent program
pairs (e.g., \texttt{right 360} vs no-op, \texttt{forward d; backward d} vs
no-op) and assert identical verification outcomes to detect encoding drift.
\item \textbf{Property fuzzer.} Randomly synthesize compound properties over
$(x,y,\texttt{heading},\texttt{pen},\texttt{vars})$, classify via a bounded
interpreter, and flag mismatches as potential false positives/negatives.
\item \textbf{Adversarial grid tests.} Craft programs that leave the 15-degree
grid or hit \texttt{heading}=360 and ensure the tool reports \texttt{UNKNOWN},
not spurious \texttt{PASSED}.
\item \textbf{Symmetry checks.} Mirror/rotate programs and properties across
axes and verify that outcomes transform predictably, catching asymmetries in
the encoding.
\item \textbf{Model-to-trace validator.} Decode Z3 models into traces and
re-check each step against the operational semantics to eliminate spurious
models.
\item \textbf{Compound properties.} Build test programs with properties that
combine geometric bounds, pen state, and user variables (e.g.,
``in box $\land$ pen up $\land$ fuel $\ge 0$'') and verify that the solver can
prove conjunctions without fragile splitting.
\item \textbf{Canvas-marking tests.} Introduce regression cases where the
expected outcome is ``region $R$ is never marked'' and ``region $S$ is always
marked when reached'', stressing the interaction of motion, pen state, and
state predicates.
\item \textbf{Semantic cross-checks.} For select programs, run a bounded
interpreter to generate traces and assert agreement with CHC verdicts (PASSED
implies no violating trace within bounds; FAILED implies a concrete violating
trace).
\item \textbf{Stress and scalability.} Add deep-loop and large-nesting programs
with combined arithmetic and geometry, then track build time, solve time, and
\texttt{UNKNOWN} rate to quantify improvements.
\item \textbf{Mode correctness.} Validate that \texttt{default},
\texttt{universal}, \texttt{safety-range}, and \texttt{specific} behave as
documented by checking initial-state constraints and ghost-parameter behavior
under controlled fixtures.
\end{enumerate}


\subsection{Extensions}
\begin{enumerate}[leftmargin=*]
\item \textbf{Exact marked-region extraction.} Compute the sets of boxes that
are \emph{guaranteed marked}, \emph{possibly marked}, and \emph{guaranteed
unmarked}, and expose them as a first-class artifact for downstream queries.
\item \textbf{Spatial coverage queries.} Support questions like ``which boxes
can be marked within $N$ steps'' and ``which boxes are inevitably marked'',
bridging reachability and inevitability.
\item \textbf{Temporal properties.} Add a small always/eventually fragment for
properties such as ``eventually pen up after drawing'' or ``always inside a
region after step $k$''.
\item \textbf{Counterexample-guided refinement.} When \texttt{UNKNOWN}, split
heading buckets or add strengthening lemmas automatically based on the model.
\item \textbf{User-defined invariant templates.} Allow lightweight inductive
sketches to steer SPACER and reduce timeouts on complex properties.
\item \textbf{Canvas region accounting.} Extend the semantics to identify
\emph{which} discrete boxes/cells on the canvas are guaranteed to be marked,
possibly marked, or guaranteed unmarked. Expose this as a queryable artifact
and allow properties like ``only these boxes are ever drawn''.
\item \textbf{Property macros with quantifiers.} Add higher-level predicates
such as \texttt{in\_box}, \texttt{distance<=r}, \texttt{never\_draws(R)}, and
\texttt{pen\_down\_only\_in(S)}, compiled to CHC constraints to reduce user
error and support compound properties.
\item \textbf{Parametric verification.} Generalize \texttt{specific} mode to
intervals and symbolic ranges, enabling sensitivity analysis and ``for all
starts in range'' guarantees.
\item \textbf{Efficient motion encoding.} Replace expensive nonlinear trig with
sound, piecewise-linear over-approximations per heading bucket, then measure
\texttt{UNKNOWN} reductions on heading-heavy programs.
\item \textbf{Invariant synthesis hooks.} Add optional linear templates and
lightweight candidate generation to strengthen invariants before CHC queries.
\end{enumerate}



\end{document}
